Fractional Types

### 2013-06-01 summer13/frac2.tex
added summer stuff

%subcode{proof} include main
%@ c : A1 * B2 <-> B1 * A2
%@@ \hat{c} : (B1 |--> A1) <=> (B2 |--> A2)

@@

%subcode{proof} include main
%@ \exists v0 : C. c <v_{in}, v> = <v_{out}, v>
%@@ (trace_v c) v_{in} = v_{out}

This is easily reversible: {{(trace_v c)dagger = trace_v c
dagger}}\footnote{Also need to prove this.}.

@@

Now that we have the trace combinator defined, we can proceed with defining
higher-order combinators. Note that this parameterizes our definition of
{{\hat{c}}} by {{v}}, the value of type {{A}} (or equivalently, type {{B}}) used
in the trace:

%subcode{proof} include main
%@ c : A1 * B2 <-> B1 * A2
%@@ \hat{c}_v : (B1 |--> A1) <=> (B2 |--> A2)

\noindent
We want this to be a transformation on combinators, taking a combinator of type
{{B1 <-> A1}} to a combinator of type {{B2 <-> A2}}. This can be achieved by
letting the combinator {{\hat{c}_v c'}} be {{trace_v (c ; c' * id)}}, where {{c
: B1 <-> A1}} and {{v : A1}}.

@@

\item {{(B |--> A) / (D |--> C) = (A * D) |--> (B * C)}}, with {{{[c1]}_{v1} :
((B |--> A) <=> (D |--> C)) / {[c2]}_{v_2} : ((B' |--> A') <=> (D' |--> C')) =
{[shuffle ; c1 * c2 dagger ; shuffle]}_{<v1, c2 v2>} : B1 * A2 |--> A1 * B2 <=>
D1 * C2 |--> C1 * D2}}, where {{shuffle : (A * B) * (C * D) <-> (A * C) * (B *
D)}}.

>>>>

%subcode{proof} include main
%@ c : A1 * B2 <-> B1 * A2
%@@ {[c]} : (B1 |--> A1) <=> (B2 |--> A2)

@@

%subcode{proof} include main
%@ exists v0 : C. c <v_{in}, v> = <v_{out}, v>
%@@ (trace_v c) v_{in} = v_{out}

This is easily reversible: {{(trace_v c)dagger = trace_v (c dagger)}}
\footnote{Also need to prove this.}.

@@

Now that we have the trace combinator defined, we can proceed with defining
higher-order combinators. Note that this parameterizes our definition of
$\{c\}$ by {{v}}, the value of type {{A}} (or equivalently, type {{B}}) used
in the trace:

%subcode{proof} include main
%@ c : A1 * B2 <-> B1 * A2
%@@ {[c]}_v : (B1 |--> A1) <=> (B2 |--> A2)

\noindent
We want this to be a transformation on combinators, taking a combinator of type
{{B1 <-> A1}} to a combinator of type {{B2 <-> A2}}. This can be achieved by
letting the combinator {{{[c]}_v c'}} be {{trace_v (c ; c' * id)}}, where
{{c : B1 <-> A1}} and {{v : A1}}.

@@

\item {{(B |--> A) / (D |--> C) = (A * D) |--> (B * C)}}, with

{{{[c1]}_{v1} : ((B |--> A) <=> (D |--> C)) / {[c2]}_{v_2} : ((B' |--> A') <=> (D' |--> C')) = {[shuffle ; c1 * c2dagger ; shuffle]}_{<v1, c2 v2>}}}
%%: B1 * A2 |--> A1 * B2 <=> D1 * C2 |--> C1 * D2}},
where
{{shuffle : (A * B) * (C * D) <-> (A * C) * (B * D)}}.
